---
title: "Patient Cost and High Value Healthcare"
author: "Mike"
date: "2/11/2020"
output: 
  html_document:
    toc: TRUE
    keep_md: TRUE


---

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

## Executive Summary

With an increasingly competitive healthcare market, systems will be forced to compete on value. By increasing provider value and lowering cost to the patient (patient burden) Froedtert can maximize its competitiveness in the regional market.

## Case Prompt

*Acutely aware of the challenges outlined above hospital executives and clinical leaders are interested seeing the “Medicare Value Story” – a data-driven narrative about Medicare population trends. The core questions articulated by the executives are detailed below: 
How does [Hospital system A] compare to other health systems across the country when it comes to Medicare population trends (quality metrics, volume metrics, and cost metrics)? Where is the system doing well and where do we have opportunities to improve? What additional insights can we derive from analyzing the large troves of public Medicare data provided by the Centers for Medicare and Medicaid (CMS)?*




```{r, include=FALSE}


library(caret)
library(tidyverse)
library(DataExplorer)
library(xgboost)
library(ggcorrplot)
library(readr)
library(reshape2)
library(fastDummies)
library(WVPlots)
library(ROCR)
library(gridExtra)
library(reshape2)
library(knitr)

hspdata <- read_csv("Data/Medicare Spending by Claim.csv")
drgdata <- read_csv("Data/Medicare_Provider_Charge_Inpatient_DRGALL_FY2016.csv")
serdata <- read_csv("Data/Provider Value of Care - Hospital.csv")
zipdata <- read_csv("Data/Zip.csv")
DRGtoMDC <- read_csv("Data/DRGtoMDCfulltable.csv")

#Create column of FH locations in dataset
drgdata$FH <- (ifelse(drgdata$ProviderId == '520177', "Yes", 
                     (ifelse(drgdata$ProviderId == '520103', "Yes", 
                     (ifelse(drgdata$ProviderId == '520063', "Yes", "No"))))))

#parse the drg ID into the first 3 numbers as drg ID
drgdata$drgID <- substr(drgdata$DRGDefinition, start = 1, stop = 3)

##To create column with FH DRG's' in the drgdata dataset
#drgdata$FHdrgID <- (ifelse(drgdata$FH %in% "Yes", drgdata$drgID, ""))

#subset drgs in the FH data select=c(drgID,ProviderName) to add hospital name
FHdrgs <- subset(drgdata, FH %in% "Yes", select=c(drgID)) 

#create flag of all drgs that match with FH data in the dataset (******************************This might not work as expected?)
#might want to try the following: drgdata$MDC <- DRGtoMDc$MDC[match(drgdata$drgID, DRGtoMDc$`MS-DRG`)]
drgdata$FHdrgflag <- (ifelse(drgdata$drgID %in% FHdrgs$drgID, "Yes", "No"))

#create flag of all drgs matching FH data from wisconsin
drgdata$WI <- (ifelse(drgdata$ProviderState == 'WI' & drgdata$FHdrgflag == 'Yes', "Yes", "No"))

#Convert dollars to numeric values: 
drgdata$ACC <- parse_number(drgdata$AverageCoveredCharges)
drgdata$ATP <- parse_number(drgdata$AverageTotalPayments)
drgdata$AMP <- parse_number(drgdata$AverageMedicarePayments)

#Find average per discharge (ex: ACC/Total discharge)

drgdata$ACCperDischarge <- (drgdata$ACC / drgdata$TotalDischarges)
drgdata$ATPperDischarge <- (drgdata$ATP / drgdata$TotalDischarges)
drgdata$AMPperDischarge <- (drgdata$AMP / drgdata$TotalDischarges)


#Find % of total bill paid by CMS AMP/ACC * 100, rounded two places

drgdata$PercentCMSperDischarge <- ((drgdata$AMPperDischarge / drgdata$ACCperDischarge) *100)
drgdata$PercentCMSperDischarge <- format(round(drgdata$PercentCMSperDischarge, 2), nsmall = 2)


```

## Data Wrangling

Once the datasets are loaded, we use the “Medicare Provider Charge Inpatient DRG ALL FY 2016” (DRG Dataset) to calculate the average covered charges, total payments, and Medicare payments. These are also calculated per discharge to find the percent of the total bill paid by CMS. Patient cost burden was determined calculating the difference between the “Average Total Payments” and “Average Medicare Payments” to arrive at the remaining patient balance. 


```{r, echo=FALSE, results='asis'}
kable(drgdata[1:1, ], caption = "Medicare Provider Charge Inpatient data FY2016")
```

***


In order to fairly compare provider value to DRG, the DRG dataset was mapped to their corresponding Major Diagnostic Category (MDC). Similarly the provider dataset (display id AMI/HF/PN/HIP) was mapped to MDC. Only the following DRG/MCD ranges were conserved across both datasets used for further comparison: 
<br>


Designate Payment measure ID with MDC value | (MDC ID xxx DRG Range)
------------ | -------------
04	Diseases and Disorders of the Respiratory System |	163 - 208
05	Diseases and Disorders of the Circulatory System |	215 - 316
08	Diseases and Disorders of the Musculoskeletal System And Connective Tissue |453 - 566

<br>

In the "Provider Value of Care - Hospital"  (SER Data) dataset, the Medicare "Value of Care Category" is translated into a numerical risk score. This forms the indication of value used throughout the analysis (see script for translation details). High value providers were any who achieved a combined average score of >= 7.


```{r, echo=FALSE, results='asis'}
kable(serdata[1:1, ], caption = "Provider Value of Care - Hospital")
```

***



```{r, include=FALSE}


#########################################
#                                       #
# Provider Quality Data Transformation  #
#                                       #
#########################################


#Create numerical scores based off value of care category
#See Quality Rank score Table reference below for detail
serdata$QualityScore <- (ifelse(grepl("Not Available", serdata$Valueofcarecategory), 'N/A',
                         ifelse(grepl("Average mortality and average payment", serdata$Valueofcarecategory), '5',
                         ifelse(grepl("Average mortality and higher payment", serdata$Valueofcarecategory), '2.5',
                         ifelse(grepl("Average complications and average payment", serdata$Valueofcarecategory), '5',
                         ifelse(grepl("Average mortality and lower payment", serdata$Valueofcarecategory), '7.5',
                         ifelse(grepl("Worse complications and higher payment", serdata$Valueofcarecategory), '0',
                         ifelse(grepl("Worse mortality and average payment", serdata$Valueofcarecategory), '2.5',
                         ifelse(grepl("Better mortality and higher payment", serdata$Valueofcarecategory), '5',
                         ifelse(grepl("Average complications and higher payment", serdata$Valueofcarecategory), '2.5',
                         ifelse(grepl("Average complications and lower payment", serdata$Valueofcarecategory), '7.5',
                         ifelse(grepl("Worse mortality and higher payment", serdata$Valueofcarecategory), '0',
                         ifelse(grepl("Better mortality and average payment", serdata$Valueofcarecategory), '7.5',
                         ifelse(grepl("Worse mortality and lower payment", serdata$Valueofcarecategory), '5',
                         ifelse(grepl("Better mortality and lower payment", serdata$Valueofcarecategory), '10',
                         ifelse(grepl("Better complications and lower payment", serdata$Valueofcarecategory), '10',
                         ifelse(grepl("Worse complications and lower payment", serdata$Valueofcarecategory), '5',
                         ifelse(grepl("Better complications and average payment", serdata$Valueofcarecategory), '7.5',
                         ifelse(grepl("Worse complications and average payment", serdata$Valueofcarecategory), '2.5',
                         ifelse(grepl("Better complications and higher payment", serdata$Valueofcarecategory), '5', 'NULL'))))))))))))))))))))


serdata$QualityScore <- as.numeric(serdata$QualityScore)

#Designate Payment measure ID with MDc value (MDc ID xxx DRG Range)
#04	Diseases and Disorders of the Respiratory System	163 - 208
#05	Diseases and Disorders of the Circulatory System	215 - 316
#08	Diseases and Disorders of the Musculoskeletal System And Connective Tissue	453 - 566

serdata$MDC <- (ifelse(grepl("PAYM_30_AMI", serdata$PaymentmeasureID), '05',
                 ifelse(grepl("PAYM_30_HF", serdata$PaymentmeasureID), '05',
                 ifelse(grepl("PAYM_90_HIP_KNEE", serdata$PaymentmeasureID), '08',
                 ifelse(grepl("PAYM_30_PN", serdata$PaymentmeasureID), '04', 'N/A')))))
#measure name might be handy for graphs
serdata$measurename <- (ifelse(grepl("PAYM_30_AMI", serdata$PaymentmeasureID), 'Heart Attack',
                               ifelse(grepl("PAYM_30_HF", serdata$PaymentmeasureID), 'Heart Failure',
                               ifelse(grepl("PAYM_90_HIP_KNEE", serdata$PaymentmeasureID), 'Hip and Knee',
                               ifelse(grepl("PAYM_30_PN", serdata$PaymentmeasureID), 'Pneumonia', 'N/A')))))


#Map DRGs to their MDc
drgdata$MDC <- DRGtoMDC$MDC[match(drgdata$drgID, DRGtoMDC$`MS-DRG`)]

#create subset of needed columns to merge with drg dataset
colnames(serdata)[colnames(serdata)=="ProviderID"] <- "Provider_ID"
serdata.subset <- serdata[c("Provider_ID","QualityScore","MDC","measurename")]

#Left Join DRG and SER subset columns
colnames(drgdata)[colnames(drgdata)=="ProviderId"] <- "Provider_ID"
drgdata$Provider_ID <- as.numeric(drgdata$Provider_ID)
drgdata$PercentCMSperDischarge <- as.numeric(drgdata$PercentCMSperDischarge )
drg.ser <- drgdata %>% left_join(serdata.subset, by=c("Provider_ID", "MDC"))

FH.drg.ser <- drg.ser %>% filter(FH == "Yes")
WI.drg.ser <- drg.ser %>% filter(ProviderState == "WI")


# fh.drg.ser.plot <- ggplot(data=subset(FH.drg.ser, !is.na(QualityScore)), aes(x=QualityScore, y=PercentCMSperDischarge, color=measurename, ... = fill=measurename)) + 
#                    geom_jitter() + 
#                    scale_y_continuous() +
#                    scale_color_manual(values=c("#ff0000", "#ffaa00","#696870","#0d00ff")) +
#                    labs(title="Quality score by percent CMS reimbursement and measure (FH)")


```



The Medicare spending by claim (HSP) dataset is transformed to match payment episode period and claim type back to the Medicare Hospital Spending (DRG) dataset above. 


```{r, echo=FALSE, results='asis'}
kable(hspdata[1:1, ], caption = "Medicare Spending by Claim")
```

***

```{r, include=FALSE}

#########################################
#                                       #
# Hospital Data Transformation          #
#                                       #
#########################################


#Can I break down the differences in percent of spending with the value from the provider dataset
#cant really relate it to the DRG, but if we find where we have the most opportunity it could differentiate the high and low value
#performers according to % of spend?

colnames(hspdata)[colnames(hspdata)=="PROVIDER_ID"] <- "Provider_ID"

#Shorten column values for recasting
hspdata$PERIOD <- (ifelse(grepl("1 to 3 days Prior to Index Hospital Admission", hspdata$PERIOD), 'Before',
                    ifelse(grepl("During Index Hospital Admission", hspdata$PERIOD), 'During',
                    ifelse(grepl("1 through 30 days After Discharge from Index Hospital Admission", hspdata$PERIOD), 'After',
                    ifelse(grepl("Complete Episode", hspdata$PERIOD), 'Total', 'N/A')))))


hspdata$CLAIM_TYPE <- (ifelse(grepl("Home Health Agency", hspdata$CLAIM_TYPE), 'HomeHealth',
                              ifelse(grepl("Skilled Nursing Facility", hspdata$CLAIM_TYPE), 'SkilledRN',
                              ifelse(grepl("Durable Medical Equipment", hspdata$CLAIM_TYPE), 'DME',
                              ifelse(grepl("Inpatient", hspdata$CLAIM_TYPE), 'IP',
                              ifelse(grepl("Outpatient", hspdata$CLAIM_TYPE), 'OP',
                              ifelse(grepl("Carrier", hspdata$CLAIM_TYPE), 'Carrier', 
                              ifelse(grepl("Hospice", hspdata$CLAIM_TYPE), 'Hospice',
                              ifelse(grepl("Total", hspdata$CLAIM_TYPE), 'Total', 'N/A')))))))))


#recast long form into wide
hspdata.original <- hspdata
hsp.recast <- recast(hspdata, Provider_ID ~ variable + CLAIM_TYPE + PERIOD, id.var = c("Provider_ID", "CLAIM_TYPE", "PERIOD"))
hsp.no.duplicate <- hsp.recast[!duplicated(as.list(hsp.recast))]

```



```{r, include=FALSE}
######################################### (Pick one)
#                                       #
#        Getting a Little Boost         #
#                                       #
#########################################

#Providervalues <- drg.ser[c("Provider_ID","HighValue")]
#HSP.xgb <- hsp.no.duplicate[-c(2,3,108,109)]

#despite converting the long form to wide above, I'm going to redo it here expressly for model creation to make removing columns easier

HSP.xgb <- subset(hspdata.original, select = -c(HOSPITAL_NAME, STATE, START_DATE, END_DATE,
                                                AVG_SPNDG_PER_EP_STATE,AVG_SPNDG_PER_EP_NATIONAL, PERCENT_OF_SPNDG_STATE,
                                                PERCENT_OF_SPNDG_NATIONAL))

hsp.recast.xgb <- recast(HSP.xgb, Provider_ID ~ variable + CLAIM_TYPE + PERIOD, id.var = c("Provider_ID", "CLAIM_TYPE", "PERIOD"))

#comparison <- setdiff(hsp.recast.xgb, HSP.xgb)
#Error: not compatible: Cols in x but not y: `PERCENT_OF_SPNDG_HOSPITAL_SkilledRN_During`, `AVG_SPNDG_PER_EP_HOSPITAL_OP_During`, 
#`AVG_SPNDG_PER_EP_HOSPITAL_Hospice_During`, `AVG_SPNDG_PER_EP_HOSPITAL_SkilledRN_During`, `PERCENT_OF_SPNDG_HOSPITAL_Hospice_During`, 
#`PERCENT_OF_SPNDG_HOSPITAL_OP_During`
#Those columns all contain duplicate data but shouldn't be removed, so just rename the data frame. 
#HSP.xgb <- hsp.recast.xgb[!duplicated(as.list(hsp.recast.xgb))]
HSP.xgb <- hsp.recast.xgb

#Average value scores by provider (funs is depreicated, but list is generating an error, I'm going to just live with this for now)
serdata.sub.xgb <- serdata.subset %>% group_by(Provider_ID) %>% summarise_at(vars(-MDC,-measurename), funs(mean(., na.rm=TRUE)))

serdata.sub.xgb$QualityScore <- as.numeric(serdata.sub.xgb$QualityScore)
#high Value care boolean for values >7:
serdata.sub.xgb$Highvalue <- (ifelse(serdata.sub.xgb$QualityScore >= 7, 1,0))

#Join the high value flag with the HSP data and remove the quality score column (no longer needed, easier to do it here)
HSP.xgb <- HSP.xgb %>% left_join(serdata.sub.xgb, by=c("Provider_ID"))
#HSP.xgb <- subset(HSP.xgb, select = -c(QualityScore))#, Provider_ID))


#remove % which creates list of factors
HSP.xgb <- lapply(HSP.xgb, gsub, pattern='%', replacement='')

#convert factors to numeric
HSP.xgb <- lapply(HSP.xgb, function(x) as.numeric(as.character(x)))

# convert list back to data frame, remove NA values
HSP.xgb <- as.data.frame(HSP.xgb)
HSP.xgb <- na.omit(HSP.xgb)
#HSP.xgb$Highvalue <- as.factor(HSP.xgb$Highvalue)
HSP.xgb.w.ser <- HSP.xgb
HSP.xgb <- subset(HSP.xgb, select = -c(Provider_ID, QualityScore))


# Move label column to first position
HSP.xgb <- HSP.xgb %>% select(Highvalue, everything())

#HSP.xgb.matrix <- data.matrix(HSP.xgb)

#Break into 70/30 test and training subsets:
set.seed(1234)
smp_size <- floor(0.70 * nrow(HSP.xgb))
set.seed(1234)
train_ind <- sample(seq_len(nrow(HSP.xgb)), size = smp_size)
train <- HSP.xgb[train_ind,]
test <- HSP.xgb[-train_ind,]


x.train = as.matrix(train)
x.train.hv <- as.factor(train$Highvalue)
y.test = as.matrix(test)

## XGBoost
# y <- subset(train, select = c(Highvalue))
# x <- subset(train, select = -c(Highvalue))
# x <- as.matrix(x)
# #y <- as.matrix(y)
# y <- as.factor(y)


#                              ----------------------------ADDITIONAL XGB TUNING HERE PLEASE
# https://www.kaggle.com/c/grupo-bimbo-inventory-demand/discussion/23170

# Caret XGB Implementation for best tune parameters
xgb_grid = expand.grid(
  nrounds = 50,
  eta = c(0.1, 0.05, 0.01),
  max_depth = c(2, 3, 4, 5, 6, 8, 10, 12),
  gamma = 0,
  colsample_bytree=1,
  min_child_weight=c(1, 2, 3, 4 ,5),
  subsample=1
)

control <- trainControl(method ="cv", number = 5)
set.seed(333)
xgb_caret <- train(x=x.train[,-c(1)], 
                   y=x.train.hv, 
                   method='xgbTree', 
                   trControl= control, 
                   tuneGrid=xgb_grid) 




#nrounds max_depth eta gamma colsample_bytree min_child_weight subsample
#111      50        10 0.1     0                1                1         1


set.seed(333)
bst <- xgboost(data = x.train[,-c(1)],
               label = x.train[,c(1)],
               max.depth = 10,
               eta = 0.1,
               nthread = 6, 
               nrounds = 50,
               early_stopping_rounds = 3,
               min_child_weight=1,
               objective = "binary:logistic")



####MERGE HERE

set.seed(333)
importance <- xgb.importance(model = bst)
#importance


#prediction on the test set:
set.seed(333)
pred <- predict(bst, as.matrix(y.test[,-c(1)]))
#convert regression into binary classification:
prediction <- as.numeric(pred > 0.5)
err <- mean(as.numeric(pred > 0.5) != test$Highvalue)
#print(paste("test-error=", err))

#ROC
pred1 <- prediction(prediction, test$Highvalue)
perf1 <- performance(pred1, "tpr", "fpr")
#plot(perf1)
#abline(a=0, b= 1)


pred1.auc = performance(pred1, measure = "auc", fpr.stop=0.1)
#pred1.auc@y.values


```



```{r, include=FALSE}


######################################### (Pick one)
#                                       #
#    This seems like a regression       #
#                                       #
#########################################

glm.data <- HSP.xgb


#check and remove zero or near zero variance features 
nzv <- nearZeroVar(glm.data, saveMetrics = FALSE)
glm.data.nzv <- glm.data[,-nzv]
glm.data.nzv <- lapply(glm.data.nzv, function(x) as.numeric(as.character(x)))
glm.data.nzv <- as.data.frame(glm.data.nzv)

# Create correlation table to find highly correlated features. Remove those with > 0.75 correlation
# to prevent multicollinearity 
glm.data.nzv.cor <- cor(glm.data.nzv)
summary(glm.data.nzv.cor[upper.tri(glm.data.nzv.cor)])
set.seed(333)
glmdnc <- findCorrelation(glm.data.nzv.cor, cutoff = .75)
glm.data.nzv.nocor <- glm.data.nzv[,-glmdnc]

# Center and Scale values
glm.data.nzv.nocor.hv <- subset(glm.data.nzv.nocor, select = c(Highvalue))
glm.data.nzv.nocor <- subset(glm.data.nzv.nocor, select = -c(Highvalue))

set.seed(333)
glm.data.preprocess <- preProcess(glm.data.nzv.nocor, method = c("center","scale"))
set.seed(333)
glm.preprocess <- predict(glm.data.preprocess,glm.data.nzv.nocor)
glm.preprocess$Highvalue <- glm.data.nzv.nocor.hv$Highvalue
glm.preprocess$Highvalue <- as.factor(glm.preprocess$Highvalue)

# Create random 70/30 training and testing dataset
set.seed(333)
smp_size <- floor(0.70 * nrow(glm.preprocess))
set.seed(333)
train_ind <- sample(seq_len(nrow(glm.preprocess)), size = smp_size)
glm.train <- glm.preprocess[train_ind,]
glm.test <- glm.preprocess[-train_ind,]


# Below, testing several different models to find the best accuracy

#glm <- glm(Highvalue~., data = glm.train, family = "binomial")
#summary(glm)


control <- trainControl(method ="repeatedcv", number = 10)
metric <- "Accuracy"
#model <- train(Highvalue~., data=glm.train, method="lvq", preProcess="scale", trControl=control)
#importance.lvq <- varImp(model, scale=FALSE)
#test <- as.data.frame(test)
#print(importance.lvq)

set.seed(333)
fit.glm <- train(Highvalue~., data = glm.train, method="glm", metric=metric, trControl=control)
set.seed(333)
fit.lda <- train(Highvalue~., data = glm.train, method="lda", metric=metric, trControl=control)
set.seed(333)
fit.cart <- train(Highvalue~., data = glm.train, method="rpart", metric=metric, trControl=control)
set.seed(333)
fit.knn <- train(Highvalue~., data = glm.train, method="knn", metric=metric, trControl=control)
set.seed(333)
fit.svm <- train(Highvalue~., data = glm.train, method="svmRadial", metric=metric, trControl=control)
set.seed(333)
fit.rf <- train(Highvalue~., data = glm.train, method="rf", metric=metric, trControl=control)

results <- resamples(list(lda=fit.lda,cart=fit.cart,knn=fit.knn, svm=fit.svm,rf=fit.rf,glm=fit.glm))
#summary(results)

# dot plot comparison of accuracy from all models
scales <- list(x=list(relation="free"), y=list(relation="free"))
#dotplot(results, scales=scales)

importance.rf <- varImp(fit.rf, scale = FALSE)
#plot(importance.rf)
#View(fit.rf)

importance.lda <- varImp(fit.lda, scale = FALSE)

```

```{r, include=FALSE}

######################################### (Used)
#                                       #
#       Split violin plotting           #
#                                       #
#########################################

GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
                             data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
                             grp <- data[1, "group"]
                             newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
                             newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
                             newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
                             
                             if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
                               stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
                                                                         1))
                               quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
                               aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
                               aesthetics$alpha <- rep(1, nrow(quantiles))
                               both <- cbind(quantiles, aesthetics)
                               quantile_grob <- GeomPath$draw_panel(both, ...)
                               ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
                             }
                             else {
                               ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
                             }
                           })

geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
                              show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}


#Create column of FH locations in dataset
HSP.xgb.w.ser$FH <- (ifelse(HSP.xgb.w.ser$Provider_ID == '520177', "Froedtert", 
                     (ifelse(HSP.xgb.w.ser$Provider_ID == '520103', "Froedtert", 
                     (ifelse(HSP.xgb.w.ser$Provider_ID == '520063', "Froedtert", "Non-Froedtert"))))))

#this might not work but trying for graphing
HSP.xgb.w.ser$local <- (ifelse(HSP.xgb.w.ser$Provider_ID == '520177', "FH", 
                         (ifelse(HSP.xgb.w.ser$Provider_ID == '520103', "FH-CMH", 
                         (ifelse(HSP.xgb.w.ser$Provider_ID == '520063', "FH-SJH",
                         (ifelse(HSP.xgb.w.ser$Provider_ID == '520138', "Aurora St Lukes",
                         (ifelse(HSP.xgb.w.ser$Provider_ID == '520139', "Aurora West Allis",
                         (ifelse(HSP.xgb.w.ser$Provider_ID == '520051', "Columbia St Marys", "Non-Local"))))))))))))

HSP.xgb.w.ser$Highvalue <- (ifelse(HSP.xgb.w.ser$Highvalue == '1', "High Value", "Non-Value"))

```


```{r, include=FALSE}
######################################### (Shown)
#                                       #
#      XGB Split violin plotting        #
#                                       #
#########################################

top5features <- subset(HSP.xgb.w.ser, select = c(AVG_SPNDG_PER_EP_HOSPITAL_Carrier_Before,
                                                  AVG_SPNDG_PER_EP_HOSPITAL_Total_Total,
                                                  AVG_SPNDG_PER_EP_HOSPITAL_Hospice_After,
                                                  AVG_SPNDG_PER_EP_HOSPITAL_IP_After,
                                                  PERCENT_OF_SPNDG_HOSPITAL_IP_During,
                                                  Highvalue, FH))

colnames(top5features)[colnames(top5features)=="AVG_SPNDG_PER_EP_HOSPITAL_Carrier_Before"] <- "Avg spending per carrier claim before admission"
colnames(top5features)[colnames(top5features)=="AVG_SPNDG_PER_EP_HOSPITAL_Total_Total"] <- "Avg episode spending total"
colnames(top5features)[colnames(top5features)=="AVG_SPNDG_PER_EP_HOSPITAL_Hospice_After"] <- "Avg spending per hospice claim after admission"
colnames(top5features)[colnames(top5features)=="AVG_SPNDG_PER_EP_HOSPITAL_IP_After"] <- "Avg ep spending per IP claim after admission"
colnames(top5features)[colnames(top5features)=="PERCENT_OF_SPNDG_HOSPITAL_IP_During"] <- "Percent of spending on IP during admission"

#hsp.xgb.box <- top10features %>% gather(-Highvalue, key = "var", value = "value") %>% ggplot(aes(x=as.factor(Highvalue), y = value)) + geom_boxplot(width=0.1) +facet_wrap(~ var, scales = "free")

hsp.xgb.violin <- top5features %>% gather(-Highvalue, -FH, key = "var", value = "value") %>% 
                                    ggplot(aes(x=as.factor(Highvalue), y = value, fill = FH)) + 
                                    geom_split_violin() + 
                                    geom_boxplot(width=0.2) + 
                                    facet_wrap(~ var, scales = "free") +
                                    scale_fill_manual(values = c("#094897","#398c1d"), 
                                                      name = "Hospital", 
                                                      labels = c("Hospital A", "High Value"))



```


```{r, include=FALSE}

######################################### (Not used)
#                                       #
#       GLM Split violin plotting       #
#                                       #
#########################################


glm.top10features <- subset(HSP.xgb.w.ser, select = c(AVG_SPNDG_PER_EP_HOSPITAL_SkilledRN_After,
                                                      PERCENT_OF_SPNDG_HOSPITAL_IP_During,
                                                      PERCENT_OF_SPNDG_HOSPITAL_IP_After,
                                                      PERCENT_OF_SPNDG_HOSPITAL_SkilledRN_Before,
                                                      PERCENT_OF_SPNDG_HOSPITAL_Carrier_After,
                                                      AVG_SPNDG_PER_EP_HOSPITAL_Hospice_After,
                                                      PERCENT_OF_SPNDG_HOSPITAL_Carrier_Before,
                                                      AVG_SPNDG_PER_EP_HOSPITAL_DME_Before,
                                                      AVG_SPNDG_PER_EP_HOSPITAL_IP_Before, 
                                                      PERCENT_OF_SPNDG_HOSPITAL_HomeHealth_Before,
                                                      Highvalue, FH))

colnames(glm.top10features)[colnames(glm.top10features)=="AVG_SPNDG_PER_EP_HOSPITAL_SkilledRN_After"] <- "Avg spending per skilled RN claim after admission"
colnames(glm.top10features)[colnames(glm.top10features)=="PERCENT_OF_SPNDG_HOSPITAL_IP_During"] <- "Percent of spending on IP during admission"
colnames(glm.top10features)[colnames(glm.top10features)=="PERCENT_OF_SPNDG_HOSPITAL_IP_After"] <- "Percent spending per IP claim after admission"
colnames(glm.top10features)[colnames(glm.top10features)=="PERCENT_OF_SPNDG_HOSPITAL_SkilledRN_Before"] <- "Percent spending per skilled RN claim before admission"
colnames(glm.top10features)[colnames(glm.top10features)=="PERCENT_OF_SPNDG_HOSPITAL_Carrier_After"] <- "Percent spending per carrier claim After admission"
colnames(glm.top10features)[colnames(glm.top10features)=="AVG_SPNDG_PER_EP_HOSPITAL_Hospice_After"] <- "Avg spending per hospice claim after admission"
colnames(glm.top10features)[colnames(glm.top10features)=="PERCENT_OF_SPNDG_HOSPITAL_Carrier_Before"] <- "Percent spending per carrier claim before admission"
colnames(glm.top10features)[colnames(glm.top10features)=="AVG_SPNDG_PER_EP_HOSPITAL_DME_Before"] <- "Avg spending per DME claim before admission"
colnames(glm.top10features)[colnames(glm.top10features)=="AVG_SPNDG_PER_EP_HOSPITAL_IP_Before"] <- "Avg spending per IP claim before admission"
colnames(glm.top10features)[colnames(glm.top10features)=="PERCENT_OF_SPNDG_HOSPITAL_HomeHealth_Before"] <- "Percent spending per HomeHealth claim before admission"


hsp.glm.violin <- glm.top10features %>% gather(-Highvalue, -FH, key = "var", value = "value") %>% 
  ggplot(aes(x=as.factor(Highvalue), y = value, fill = FH)) + 
  geom_split_violin() + 
  geom_boxplot(width=0.1) + 
  facet_wrap(~ var, scales = "free") + 
  scale_fill_manual(values = c("#094897","#398c1d"))

#plot(hsp.glm.violin)

hsp.glm.bar.fh <- ggplot(data = glm.top10features %>% 
                         gather(-Highvalue, -FH, key = "var", value = "value"), 
                         aes(x=as.factor(Highvalue), y = value, fill = FH)) + 
                         geom_bar(position = "dodge", stat = "summary", fun.y = "mean") +
                         stat_summary(aes(label=round(..y..,2)), fun.y=mean, geom="text", size=3,vjust = -0.5) + 
                         facet_wrap(~ var, scales = "free") + 
                         scale_fill_manual(values = c("#094897","#398c1d"))

#plot(hsp.glm.bar.fh)

```


```{r, include=FALSE}
#########################################
#                                       #
#       Putting the Story Together      #
#                                       #
#########################################



glm.export <- subset(HSP.xgb.w.ser, select = c(AVG_SPNDG_PER_EP_HOSPITAL_SkilledRN_After,
                                               PERCENT_OF_SPNDG_HOSPITAL_IP_During,
                                               PERCENT_OF_SPNDG_HOSPITAL_IP_After,
                                               PERCENT_OF_SPNDG_HOSPITAL_SkilledRN_Before,
                                               PERCENT_OF_SPNDG_HOSPITAL_Carrier_After,
                                               AVG_SPNDG_PER_EP_HOSPITAL_Hospice_After,
                                               PERCENT_OF_SPNDG_HOSPITAL_Carrier_Before,
                                               AVG_SPNDG_PER_EP_HOSPITAL_DME_Before,
                                               AVG_SPNDG_PER_EP_HOSPITAL_IP_Before, 
                                               PERCENT_OF_SPNDG_HOSPITAL_HomeHealth_Before,
                                               Highvalue, FH, local, Provider_ID))

colnames(glm.export)[colnames(glm.export)=="AVG_SPNDG_PER_EP_HOSPITAL_SkilledRN_After"] <- "Avg spending per skilled RN claim after admission"
colnames(glm.export)[colnames(glm.export)=="PERCENT_OF_SPNDG_HOSPITAL_IP_During"] <- "Percent of spending on IP during admission"
colnames(glm.export)[colnames(glm.export)=="PERCENT_OF_SPNDG_HOSPITAL_IP_After"] <- "Percent spending per IP claim after admission"
colnames(glm.export)[colnames(glm.export)=="PERCENT_OF_SPNDG_HOSPITAL_SkilledRN_Before"] <- "Percent spending per skilled RN claim before admission"
colnames(glm.export)[colnames(glm.export)=="PERCENT_OF_SPNDG_HOSPITAL_Carrier_After"] <- "Percent spending per carrier claim After admission"
colnames(glm.export)[colnames(glm.export)=="AVG_SPNDG_PER_EP_HOSPITAL_Hospice_After"] <- "Avg spending per hospice claim after admission"
colnames(glm.export)[colnames(glm.export)=="PERCENT_OF_SPNDG_HOSPITAL_Carrier_Before"] <- "Percent spending per carrier claim before admission"
colnames(glm.export)[colnames(glm.export)=="AVG_SPNDG_PER_EP_HOSPITAL_DME_Before"] <- "Avg spending per DME claim before admission"
colnames(glm.export)[colnames(glm.export)=="AVG_SPNDG_PER_EP_HOSPITAL_IP_Before"] <- "Avg spending per IP claim before admission"
colnames(glm.export)[colnames(glm.export)=="PERCENT_OF_SPNDG_HOSPITAL_HomeHealth_Before"] <- "Percent spending per HomeHealth claim before admission"

DRG.HSP.SER.Export <- drg.ser %>% left_join(glm.export, by=c("Provider_ID"))

# Difference between AMP and ATP (ATP - AMP) is the patient burden/responsibility 
DRG.HSP.SER.Export$patientburden <- ((DRG.HSP.SER.Export$ATPperDischarge - DRG.HSP.SER.Export$AMPperDischarge))
#DRG.HSP.SER.Export$PercentCMSperDischarge <- format(round(drgdata$PercentCMSperDischarge, 2), nsmall = 2)


#Filter MDC's for those which match the SER/Provdier episode spending presumed MDC's
#This does limit the analysis of which drgs have the highest patient burden
#however, it allows us to make a more accurate inference as to the value spending 
#when using the provider value and hospital episode data sets. 
DRG.HSP.SER.MDCsub <- DRG.HSP.SER.Export %>% filter(MDC %in% c('05','04','08'))

high.value.subset <- DRG.HSP.SER.MDCsub %>% filter(Highvalue %in% "High Value")
non.value.subset <- DRG.HSP.SER.MDCsub %>% filter(Highvalue %in% "Non-Value")
fh.value.subset <- DRG.HSP.SER.MDCsub %>% filter(FH.y %in% "Froedtert")


#Averaging the patient burden by DRG for high value and non-value patietns (column 41 is pt burden, update to name when there is time)
high.value.drg.avg <- aggregate(high.value.subset[, 40], list(high.value.subset$DRGDefinition), mean)
non.value.drg.avg <- aggregate(non.value.subset[, 40], list(non.value.subset$DRGDefinition), mean)


colnames(high.value.drg.avg)[colnames(high.value.drg.avg)=="patientburden"] <- "High Value Patient Burden"
colnames(non.value.drg.avg)[colnames(non.value.drg.avg)=="patientburden"] <- "Non-value patient burden"

high.non.value.drg <-merge(high.value.drg.avg,non.value.drg.avg)

high.non.value.drg$delta <- (high.non.value.drg$`High Value Patient Burden` - high.non.value.drg$`Non-value patient burden`)
high.non.value.drg$Percent_Delta <- (((high.non.value.drg$`High Value Patient Burden` - high.non.value.drg$`Non-value patient burden`)/ high.non.value.drg$`High Value Patient Burden`) * 100)

#parse DRG from title
high.non.value.drg$drgID <- substr(high.non.value.drg$Group.1, start = 1, stop = 3)

#Map DRG to MDC
high.non.value.drg$MDC <- DRGtoMDC$MDC[match(high.non.value.drg$drgID, DRGtoMDC$`MS-DRG`)]

#Try to find the DRG with the biggest difference in patient burden between FH and Highvalue providers
high.FH.value.subset <- DRG.HSP.SER.MDCsub %>% filter(Highvalue %in% "High Value" | FH.y %in% "Froedtert")
colnames(high.value.drg.avg)[colnames(high.value.drg.avg)=="Group.1"] <- "DRGDefinition"

#Join the high value average patient burden per DRG to the FH only DRG's then calculate the delta between avg high value and FH
fh.high.wide <- fh.value.subset %>% left_join(high.value.drg.avg, by=c("DRGDefinition"))
fh.high.wide$delta <- (fh.high.wide$`High Value Patient Burden` - fh.high.wide$patientburden)
fh.high.wide$Percent_Delta <- (((fh.high.wide$`High Value Patient Burden` - fh.high.wide$patientburden) / fh.high.wide$`High Value Patient Burden`) * 100)



#column 40 is patient burden
fh.high.wide.mdc.avg <- aggregate(fh.high.wide[, 40], list(fh.high.wide$MDC), mean)
#column 41 is high value patient burden
fh.high.wide.mdc.avg$highvalueptburden <- aggregate(fh.high.wide[, 41], list(fh.high.wide$MDC), mean, na.action = na.omit)

high.mdc.box <- fh.high.wide %>% select(MDC, `High Value Patient Burden`) %>% 
                                 ggplot(aes(x=MDC, y=`High Value Patient Burden`)) + 
                                 labs(title="High Value and Patient Burden by MDC") +
                                 geom_boxplot() +
                                 theme(plot.title=element_text(hjust=0.5, color="white"), plot.background=element_rect(fill="#808484"), 
                                        axis.text.x=element_text(colour="white"), axis.text.y=element_text(colour="white"), 
                                        axis.title=element_text(colour="white"))

fh.mdc.box <- fh.high.wide %>% select(MDC, patientburden) %>% 
                               ggplot(aes(x=MDC, y=patientburden)) + 
                               labs(title="FH Patient Burden by MDC") +
                               geom_boxplot() +
                               theme(plot.title=element_text(hjust=0.5, color="white"), plot.background=element_rect(fill="#808484"), 
                                    axis.text.x=element_text(colour="white"), axis.text.y=element_text(colour="white"), 
                                    axis.title=element_text(colour="white"))

#grid.arrange(high.mdc.box,fh.mdc.box, ncol = 2, nrow = 1)


high.fh.mdc.box <- ggplot(fh.high.wide, aes(MDC)) +                    
                          geom_violin(aes(y=`High Value Patient Burden`), colour="blue") + 
                          geom_violin(aes(y=patientburden), colour="red", alpha = 0.5) + 
                          labs(title="Patient Cost Burden by MDC for FH and High Value Providers", 
                               subtitle="All High Value Providers as Average per MDC",
                               y="Patient Burden", 
                               x="Major Diagnostic Category", 
                               caption="Blue: High Value Providers, Red: FH") 





melt.hfhvs <- melt(fh.high.wide, id=c("DRGDefinition"), measure.vars=c("patientburden", "High Value Patient Burden"), variable.name="Provider",value.name="patientburden")
melt.hfhvs$Name <- (ifelse(melt.hfhvs$Provider %in% "patientburden", 'Froedtert',
                           ifelse(melt.hfhvs$Provider %in% "High Value Patient Burden", 'High Value', '')))
melt.hfhvs$drgID <- substr(melt.hfhvs$DRGDefinition, start = 1, stop = 3)
melt.hfhvs$MDC <- DRGtoMDC$MDC[match(melt.hfhvs$drgID, DRGtoMDC$`MS-DRG`)]


g1 <- ggplot(melt.hfhvs, aes(x = patientburden, fill = Name)) + 
              geom_density(alpha = 0.7) + 
              scale_fill_manual(values = c("#094897","#398c1d"), 
                                                      name = "Hospital", 
                                                      labels = c("Hospital A", "High Value")) + 
              labs(x="Patient Burden") 

g2 <- ggplot(melt.hfhvs, aes(x = MDC, y = patientburden, fill = Name)) + 
              geom_violin(alpha = 0.7) + geom_boxplot(width=0.1) + 
              scale_fill_manual(values = c("#094897","#398c1d"), 
                                                      name = "Hospital", 
                                                      labels = c("Hospital A", "High Value")) + 
              labs(x="Major Disease Category", y="Patient Burden")


melt.hfhvs.plot.bar <- melt.hfhvs %>% select(drgID, Name, patientburden) %>% 
                        ggplot(aes(x=drgID, y=patientburden)) + 
                        theme(axis.text.x = element_text(angle = 45)) +
                        geom_col(aes(fill = Name)) + 
                        scale_fill_manual(values = c("#094897","#398c1d"), 
                                                      name = "Patient Burden by DRG", 
                                                      labels = c("Hospital A", "High Value")) +
                        
                        labs(title="Patient Burden per DRG", 
                             subtitle="[Hospital A] and National AVG High Value Proviers", 
                             y="Patient Burden", 
                             x="DRG")




```
<br>
<br>

Overview of difference in patient burden between [Hospital A] and "High Value" healthcare providers. This shows that per DRG (top), overall (lower left), and per MDC (lower right) high value providers have lower patient cost burden. [Hospital A] has 188 DRG's represented in the dataset, of those 91% (172 of 188) have opportunity for value improvement. With total payments at $121.2 million, opportunity for value improvement is just over 21 million.


<br>

```{r,echo=FALSE, warning = FALSE, fig.height=10, fig.width=14}

plot(melt.hfhvs.plot.bar)

grid.arrange(g1, g2, widths = c(4, 4),
             layout_matrix = rbind(c(1, 2)))


```

<br>
<br>

To determine the most important episode spending characteristics of high value providers, various machine learning models were employed. Data was preprocessed to remove near zero variance, and highly correlated (cutoff = 0.75) predictors, then normalized (centered and scaled) for increased regression performance. Data was randomly sampled into 70/30 training/testing subsets. All models (not XGBoost) were trained using the train function of the caret package with repeated 10-fold cross validation for accuracy in model evaluation.  <br>

## Model Comparison 

General Linear Model (GLM), Linear Discriminant Analysis (LDA), Recursive Partitioning and Regression Trees (RPART), k-nearest neighbors (KNN), Support Vector Machines (SVM), Random Forest (RF) were all evaluated for highest accuracy. (XGBoost was performed seperately using the XGBoost package and is not shown here).

```{r,echo=FALSE}

dotplot(results, scales=scales)

```



```{r, include=FALSE}


## Feature Importance (LDA)
#{r,echo=FALSE}
#plot(importance.lda)



#########################################
#                                       #
#       Final Bar Plots                 #
#                                       #
#########################################

glm.bar.final <- ggplot(data = glm.top10features %>% gather(-Highvalue, -FH, key = "var", value = "value"), 
                        aes(x=as.factor(Highvalue), y = value, fill = FH)) + 
                        geom_bar(position = "dodge", stat = "summary", fun.y = "mean") +
                        stat_summary(aes(label=round(..y..,2)), fun.y=mean, geom="text", size=3, vjust = -0.5) + 
                        facet_wrap(~ var, scales = "free") + 
                        theme(axis.text.x = element_text(angle = 45)) + 
                        scale_fill_manual(values = c("#094897","#398c1d")) 

#plot(glm.bar.final)

#Creating Dataframe of just FH and High Value providers for closer analysis
glm.bar.data <- glm.top10features
glm.bar.data$HVFH <- (ifelse(grepl("High Value", glm.bar.data$Highvalue), 'High Value',
                             ifelse(glm.bar.data$FH %in% "Froedtert", 'Froedtert', "0")))
glm.bar.HVFH <- glm.bar.data %>% filter(HVFH != "0")



bar1 <- ggplot(data=glm.bar.HVFH, aes(x=HVFH, y=`Avg spending per skilled RN claim after admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) + 
              scale_fill_manual(values = c("#094897","#398c1d")) + 
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) + 
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="Skilled RN Claim After Admission", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Average Spending", 
                   x="", 
                   caption = "1 through 30 days After Discharge from Index Hospital \n Admission, Skilled Nursing Facility Claim Type ")

bar2 <- ggplot(data=glm.bar.HVFH, aes(x=HVFH, y=`Percent of spending on IP during admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
              scale_fill_manual(values = c("#094897","#398c1d")) +  
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="IP During Admission", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Percent of Spending", 
                   x="", 
                   caption = "During Index Hospital Admission,\n Inpatient Claim Type")

bar3 <- ggplot(data=glm.bar.HVFH, aes(x=HVFH, y=`Percent spending per IP claim after admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
              scale_fill_manual(values = c("#094897","#398c1d")) +  
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="IP Claim After Admission", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Percent of Spending", 
                   x="", 
                   caption = "1 through 30 days After Discharge from Index Hospital \n Admission, Inpatient Claim Type")

#bar4 <- ggplot(data=glm.bar.HVFH, aes(x=HVFH, y=`Percent spending per skilled RN claim before admission`, fill = HVFH)) + geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
#        scale_fill_manual(values = c("#094897","#398c1d")) +  theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
#        stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
#        labs(title="Percent Spending per Skilled RN Claim Before Admission", subtitle="[Hospital A] and High Value Proviers (National AVG)",
#        y="Percent of Spending", x="")

bar5 <- ggplot(data=glm.bar.HVFH, aes(x=HVFH, y=`Percent spending per carrier claim After admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
              scale_fill_manual(values = c("#094897","#398c1d")) +  
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="Carrier Claim After Admission", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Percent of Spending", 
                   x="", 
                   caption = "1 through 30 days After Discharge from Index Hospital Admission,\n Carrier (Ambulatory and Ancillary Services) Claim Type")

bar6 <- ggplot(data=glm.bar.HVFH, aes(x=HVFH, y=`Avg spending per hospice claim after admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
              scale_fill_manual(values = c("#094897","#398c1d")) +  
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="Hospice Claim After Admission", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Average Spending", 
                   x="", 
                   caption = "1 through 30 days After Discharge from Index Hospital \n Admission, Hospice Claim Type")


#{r,echo=FALSE, fig.height=10, fig.width=12}

#grid.arrange(bar1,bar2,bar3,bar5,bar6, ncol=3, nrow=2)


```



<br>

## Feature Importance (XGBoost)

XGBoost hyperparameter tuning was perfored using the caret implementation. However, this implementation is not as performant as the native XGBoost package, which was used for the final model using the parameters below:

```{r,echo=FALSE}

xgb_caret$bestTune

```

The resulting top 10 features, in order of relative importance are shown below:

```{r,echo=FALSE, warning=FALSE}

xgb.plot.importance(importance_matrix = importance, 
                    top_n = 10, 
                    xlab = "Relative importance") 

```

## XGBoost Model Performance

XGBoost attained the highest accuracy of the models tested at 94.8%, with good sensitivity / recall (true positive rate), F1-score of 97.26% and statistical significance (P-value < 0.05%). Low specificity is not overly concerning in this application.

```{r,echo=FALSE}

# Confusion Matrix
confusionMatrix(as.factor(prediction), as.factor(test$Highvalue))

```


```{r,echo=FALSE}

# ROC #check on this

# plot(perf1)
# abline(a=0, b= 1)


```


Focusing in on the top 5 features (for brevity), Violin plots show the distribution of episode spending between high-value, and non-high value providers (FH spending shown in blue). 

```{r,echo=FALSE, fig.height=10, fig.width=14}

plot(hsp.xgb.violin)

```

```{r, include=FALSE}
 
 #########################################
#                                       #
#       XGB Final Bar Plots             #
#                                       #
#########################################

 
#Creating Dataframe of just FH and High Value providers for closer analysis
xgb.bar.data <- top5features
xgb.bar.data$HVFH <- (ifelse(grepl("High Value", xgb.bar.data$Highvalue), 'High Value',
                             ifelse(xgb.bar.data$FH %in% "Froedtert", 'Froedtert', "0")))
xgb.bar.HVFH <- xgb.bar.data %>% filter(HVFH != "0")



xgb.bar1 <- ggplot(data=xgb.bar.HVFH, aes(x=HVFH, y=`Avg spending per carrier claim before admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) + 
              scale_fill_manual(values = c("#094897","#398c1d")) + 
              scale_x_discrete(labels = c('Hospital A','High Value')) +
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) + 
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="Average Spending per Carrier Claim pre-Admission", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Average Spending", 
                   x="", 
                   caption = "1 through 30 days before Index Hospital \n Admission, Carrier (Ambulatory and Ancillary Services) Claim Type ")

xgb.bar2 <- ggplot(data=xgb.bar.HVFH, aes(x=HVFH, y=`Avg episode spending total`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
              scale_fill_manual(values = c("#094897","#398c1d")) +
              scale_x_discrete(labels = c('Hospital A','High Value')) +
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="Total Average Episode Spending", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Average Spending", 
                   x="", 
                   caption = "Index Hospital Admission,\n Total Claim Type")

xgb.bar3 <- ggplot(data=xgb.bar.HVFH, aes(x=HVFH, y=`Avg spending per hospice claim after admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
              scale_fill_manual(values = c("#094897","#398c1d")) +
              scale_x_discrete(labels = c('Hospital A','High Value')) +
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="Average Spending per Hospice Claim", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Average Spending", 
                   x="", 
                   caption = "1 through 30 days After Discharge from Index Hospital \n Admission, Hospice Claim Type")


xgb.bar5 <- ggplot(data=xgb.bar.HVFH, aes(x=HVFH, y=`Avg ep spending per IP claim after admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
              scale_fill_manual(values = c("#094897","#398c1d")) +
              scale_x_discrete(labels = c('Hospital A','High Value')) +
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="Average Spending per IP Claim post-Admission", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Average Episode Spending", 
                   x="", 
                   caption = "1 through 30 days After Discharge from Index Hospital Admission,\n InPatient Claim Type")

xgb.bar6 <- ggplot(data=xgb.bar.HVFH, aes(x=HVFH, y=`Percent of spending on IP during admission`, fill = HVFH)) + 
              geom_bar(stat="summary", fun.y = "mean", position=position_dodge()) +
              scale_fill_manual(values = c("#094897","#398c1d")) +
              scale_x_discrete(labels = c('Hospital A','High Value')) +
              theme(legend.position = "none", axis.text.x = element_text(angle = 45)) +
              stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge", width=.2) +
              labs(title="Percent Spending During IP Admission", 
                   subtitle="[Hospital A] and High Value Proviers (National AVG)",
                   y="Percent Spending", 
                   x="", 
                   caption = "During Index Hospital Admission Index, \n  Inpatient Claim Type")

```


## High Value Comparison

Comparing [Hospital A] rates to those of High-value providers only we more clearly see the areas of opportunity for reducing patient cost burden. For example, high-value providers spend more during the inpatient admission but less in total average episode spending. Additionally, [Hospital A] should more closely evaluate ways to reduce average spending in post acute care (Inpatient post-admission and hospice claims) in addition to reducing ambulatory and ancillary services prior to admission (carrier claim pre-admission).

```{r,echo=FALSE, fig.height=14, fig.width=12}

grid.arrange(xgb.bar6,xgb.bar2,xgb.bar3,xgb.bar5,xgb.bar1, ncol=2, nrow=3)

```


## Data

Datasets can be found below: <br>
DRG Data: https://data.cms.gov/inpatient-provider-lookup/view-data <br>
HSP Data: https://data.medicare.gov/Hospital-Compare/Medicare-Hospital-Spending-by-Claim/nrth-mfg3 <br>
Provider (SER): https://data.medicare.gov/Hospital-Compare/Payment-and-value-of-care-Hospital/c7us-v4mf <br>
Zip: https://public.opendatasoft.com/explore/dataset/us-zip-code-latitude-and-longitude/export/ <br>
*Note: The CSV's provided reflect modified headers (spaces removed) not included in the script here.* <br>
